---
title: "Happiness Economics - Group: Romania"
author: "[Sören Schwabbauer](soeren.schwabbauer@uibk.ac.at), [David Hollenstein](david.hollenstein@student.uibk.ac.at), [Alexander Hanser](alexander.hanser@student.uibk.ac.at), [Jürgen Bildstein](juergen.bildstein@student.uibk.ac.at)"
#date: "2022-10-25"
output: 
  html_document: 
    css: style.css
    
    toc: true
    toc_depth: 3
    toc_float: true
    
    number_sections: true

---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# load libraries
library(knitr)
library(dplyr)
library(haven)
library(ggplot2)
library(ggmosaic)
library(lazyeval)
library(gridExtra)
library(ggmosaic)
library(lemon)
library(reshape2)
library(spatstat.utils)
library(tibble)
library(webr)
library(patchwork)
library(factoextra)

if (dir.exists("G:/Geteilte Ablagen/")) {
  
  INPUT = "G:/Geteilte Ablagen/data_analytics/01_data_build/OUTPUT/"
  
} else if (dir.exists("G:/Shared drives/")) {
  
  INPUT = "G:/Shared drives/data_analytics/01_data_build/OUTPUT/"
  
}

# load dataframe
load(paste0(INPUT, "Romania.rda"))

```


```{r functions & plots for task 2 , echo = FALSE, out.width="100%"}
##### define themes and create functions for plotting ##########################

# define theme for mosaic ######################################################
mosaic_theme <-   theme( 
  #legend.position = "none",
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  axis.text.x = element_text(angle=90, size = 7),
  axis.text.y = element_text(size = 7),
  panel.background = element_rect(fill = "white"),
  panel.grid.major.y = element_line(size = 0, linetype = 'solid',
                                    colour = "white") ,
  legend.position = "none",
  plot.title = element_text(color="black", size= 8, face="bold.italic", vjust = 0.5)
) 

  
# define function, incl. theme for barplots ####################################

barplot_var <- function(var){
  romania %>%
    ggplot(aes(x= {{var}}, y= ..count.. , fill = {{var}})) +
    geom_bar() +
    labs(x = "",
         y = "total number") +
    geom_text(stat = "count", aes(label= paste0(..count.., " (", round(..count../nrow(romania),4)*100 , "%)")), vjust = -0.5, size = 3) +
  
    theme(
      legend.position = "none",
      axis.title.x = element_blank(),
      panel.background = element_rect(fill = "white"),
      panel.grid.major.y = element_line(size = 0.5, linetype = 'solid',
                                        colour = "grey") ,
      plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5)
      
    )
}


boxplot_for_barplot <- function(var){
  romania %>%
    ggplot(aes(y = as.numeric({{var}}))) +
    geom_boxplot(width = 0.5) +
    coord_flip() +
    
    theme(
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      panel.background = element_rect(fill = "white"),
      panel.grid.major.y = element_line(size = 0.5, linetype = 'solid',
                                        colour = "white"),
      plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5)
    ) 
}

boxplot_age <- function(var1, var2, var3){
  romania %>% 
    ggplot(aes(x = {{var1}}, y = {{var2}})) +
    geom_boxplot(aes(fill = {{var3}})) +
    
    theme(
      axis.title.x = element_blank(),
      axis.text.x = element_text(angle=90),
      axis.ticks.x = element_blank(),
      #axis.title.y = element_blank(),
      #axis.text.y = element_blank(),
      #axis.ticks.y = element_blank(),
      panel.background = element_rect(fill = "white"),
      panel.grid.major.y = element_line(size = 0.5, linetype = 'solid',
                                        colour = "grey"),
      plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5)
      
    ) +
    scale_y_continuous(breaks = c(10, 20, 30, 40, 50, 60, 70, 80))
}

```

```{r functions & plots for task 3 , echo = FALSE, out.width="100%"}
### function for impact of the level of trust on 
trust_var_summary <- function(var, var_char){
  romania %>% select(trust_fac, {{var}}) %>% rename(member = {{var}}) %>% mutate(cat = {{var_char}}) %>%
    group_by(member, cat, trust_fac) %>%
    summarise(n = n()) %>%
    mutate(prop = n/sum(n)) 
}


### function + plot for general membership
ties_var_summary <- function(var, var_char){
  romania %>% select({{var}},contains("member_")) %>% rename(member = {{var}}) %>% melt() %>%
    group_by(value, member) %>%
    summarise(n = n()) %>%
    mutate(prop = n/sum(n)) %>%
    
    mutate(value = replace(value, value == 1, "member"),
           value = replace(value, value == 0, "no member"),
           value = as_factor(value)) %>%
    
    ggplot(aes(x = (value), y = prop, fill = as_factor(member))) +
    geom_bar(stat = "identity") +
    labs(y = "Distribution (%)") + 
    theme(
      axis.title.x = element_blank(),
      axis.text.x = element_text(angle=0),
      #axis.title.y = element_blank(),
      panel.background = element_rect(fill = "white"),
      panel.grid.major.y = element_line(size = 0, linetype = 'solid',
                                        colour = "grey") ,
      plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5) ,
      plot.subtitle = element_text(color = "black", size = 10, face = "italic")
      
    ) +
    
    scale_y_continuous(labels = scales::percent,
                       breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) 
}

### function for each membership & type of neighbor + theme for the plots
fun_happy <- function(cat, var, var_char){
  romania %>% select({{cat}}, {{var}}) %>% rename(member = {{var}}) %>% mutate(cat = {{var_char}}) %>%
    
    mutate(member = as.character(as_factor(member)),
           member = replace(member, member == "Mentioned", "yes"),
           member = replace(member, member == "Not mentioned", "no"))
}

theme_cat <-   theme(
  axis.title.x = element_blank(),
  axis.text.x = element_text(angle=0),
  #axis.title.y = element_blank(),
  panel.background = element_rect(fill = "white"),
  panel.grid.major.y = element_line(size = 0, linetype = 'solid',
                                    colour = "grey") ,
  plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5) 
)

```

# Download data
>  Download the data for the country you choose. You also find the official variable description file in the corresponding folder.

Done.

___
# First overview of data
> Get acquainted with the data (rename and/or recode variables). The main variables with which we are going to work are measures of subjective well-being (SWB), namely general happiness and life satisfaction. Are these two variables comparable measures of SWB? How do these variables correlate with personal characteristics like income, health, age, marital status, etc.? Find suitable ways to show some possible (not necessarily causal) relationships.

## A170 satisfaction in life
```{r , echo = FALSE, out.width="100%"}
 summary(romania$satisfaction)

```
The summary command allows us to have a rough overview of the variable A170 - satisfaction in life. The variable is scaled from 1 to 10, with 10 being the highest level of satisfaction. Since one can rank the level of satisfaction (e.g: a level of 8 being higher ranked than a level 2), but the distance between the levels is subjective (e.g: a person on a level 8 is not necessarily twice as happy as a person on the level 4) Life satisfaction can be considered an ordinarily scaled variable. 
The summary command shows, that everybody has replied to to questions (no NA's). Another conclusion which can be drawn from the summary command is the average level of satisfaction. With a median level of 8, and a mean of 7.5, the Romanian people are generally not extremely satisfied, but also not unsatisfied with their life as a whole. In addition to that, it can be seen, that the half of the asked population ranks themselves between a 6 and a 9.

The following plot allows a look at the distribution of satisfaction
```{r , echo = FALSE, out.width="100%"}
bar_satiscation <- barplot_var(satisfaction_fac) 

box_satiscation <- boxplot_for_barplot(satisfaction) +
  labs(title = "Overall life satisfaction") 

grid.arrange(box_satiscation, bar_satiscation, nrow = 2, heights = c(0.5,2))
```
The barplot on the distribution of satisfaction in life adds additional information to the summary command. As one can see, most people can identify with the highest level "satisfied" . It remains unclear, why there is such a rapid drop one level below. Furthermore it can be seen, that the lower 25% are much more distributed (from 2 to 5), whereas "Satisfied" contains all the upper 25% of the counts. 

## A008 Feeling of happiness
```{r , echo = FALSE, out.width="100%"}
summary(romania$happy)
```
Also the variable happy only contains interpretable values. Neither has nobody not answered, nor has the question being skipped, or other other problems occurred. The variable is scaled from 1 to 4. 1 indicates "very happy", 4 indicates "not at all happy". Identical to satisfaction, the feeling of happiness counts as a originally scaled variable.

The following barplot allows a closer look at the distribution of happiness within # the questioned people in Romania
```{r , echo=FALSE, out.width="100%"}
barplot_var(happy_fac) +
  labs(title = "Overall feeling of happiness")
```
From the barplot one can conclude, that most people (approx. 56%) are "quite happy", one fifth of the questioned population are "very happy" and roughly the same amount of people are "not very happy", or "not at all happy"


## Univariate and multivariate analysis of SWB Factors
In the following section we are going to provide a comparison of the two key variables with other variables. 

### Income
```{r , echo = FALSE, out.width="100%"}
summary(romania$income_scale)
```
The variable income was evaluated by showing the questioned households a range of income groups within their country, of which the participants had to select one. The income then got scaled from 1 (the 1st decile) and 10 (the highest decile).

The following two plots allow an insight in the income distribution of Romania
```{r , echo = FALSE, out.width="100%"}

bar_income <- barplot_var(income_scale_fac) +
    theme(axis.text.x = element_text(angle=90))

box_income <- boxplot_for_barplot(income_scale) +
  labs(title = "Income distribution") 

grid.arrange(box_income, bar_income, nrow = 2, heights = c(0.5,2))
```
It can be seen, that the distribution is right skewed. This indicates, that the vast majority belongs to a lower income group. The boxplot shows, that 50% of the people lay in between the 3rd and the 5th decile.

The following mosaic plots shall provide an overview of the two main variables and the scaled income.
```{r , echo = FALSE, out.width="100%"}
inc_happy <-  romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(happy_fac, income_scale_fac), fill = happy_fac)) +
  
  labs(title ="Comparison of happiness in life and income",
       fill = "Scale of happiness") +
  mosaic_theme
  
inc_satis <- romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(satisfaction_group, income_scale_fac), fill = satisfaction_group)) +
  
  labs(title ="Comparison of satisfaction in life and income",
       fill = "Scale of satisfaction") +
  mosaic_theme

grid.arrange(inc_happy, inc_satis, nrow = 1)
```
The two mosaic plots allow a bivariate exploratory analysis among the variables income and happiness, as well as income and satisfaction. The comparison between income and satisfaction in life shows, that the group with the lowest income is the group has more "very happy" people, than the following 3 decile's. However by grouping "quite happy" and "very happy" into one category, as suggested by the second decile, it can then be seen that the lower three deciles make up for the lowest share. When analyzing the top 30% of income earners, we can see that almost everybody is at least "quite happy". Also worth noting is that the top decile group of earners has less "very happy" people as decile group 7,8 & 9.

For a better overview, we grouped the levels of satisfaction into 1 = "Not satisfied at all, 2-5 = "not very satisfied", 6-9 = "quiet satisfied" and 10  = very satisfied.Comparing the satisfaction and the income, the group with the lowest income, again has one of the highest rates of satisfaction. Tough it should also be mentioned, that they also share one of the highest rates of Dissatisfaction. Once again it shows, that a higher income rules out the chance of being "not satisfied at all". At the same time, the top 10% income group accounts for the lowest amount of very satisfied people. 


### Health
```{r , echo=FALSE, out.width="100%"}
bar_health <- barplot_var(health_fac) 

box_health <- boxplot_for_barplot(health) +
  labs(title = "Health distribution")

grid.arrange(box_health, bar_health, nrow = 2, heights = c(0.5,2))
```
The average citizen seems to be in rather good health condition. Most of the answers group around the "good" health answer. The second most frequent answer is the "fair" health response. A very small percentage of respondents report being of "poor" or "very poor" health. 

```{r , echo=FALSE, out.width="100%"}
health_happy <-  romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(happy_fac, health_fac), fill = happy_fac)) +
  
  labs(title ="Comparison of happiness in life and health",
       fill = "Scale of happiness") +
  mosaic_theme

health_satis <- romania %>%
  
  ggplot() +
  geom_mosaic(aes(x =  product(satisfaction_group, health_fac), fill = satisfaction_group)) +
  
  labs(title ="Comparison of satisfaction in life and health",
       fill = "Scale of happiness") +
  mosaic_theme

grid.arrange(health_happy, health_satis, nrow = 1)
```
These mosaic plots show a connection between health of an individual and the satisfaction with life and overall happiness. Looking at happiness in life first, what stands out is, that those with poor and very poor health are to a large extent not very happy. This also translates to overall life satisfaction. Those with poor health are to a large extent not very satisfied. The opposite to this observation also holds true. Those with good and very good health are to a very large extent either very happy or quite happy. Respectively, those with good and very good health are also quite satisfied and very satisfied.

### Age
```{r , echo=FALSE, out.width="100%"}
summary(romania$age)
```
The summary command tells us the mean and the median age. Bothe are around 50. With the mean and the median age laying close together, one can say, that  the distribution is rater equal. Since the age scaling end at the age of 82, one can not say, how old the oldest person in the dataframe is. The youngest however is at the age of 19.

In order to get a brief overview of the age distribution, a population pyramid can help.
```{r , echo=FALSE, out.width="100%"}
romania %>% 
  group_by(age, sex_fac) %>%
  summarize(n = n()) %>% 
  mutate(age = as.character(age),
         sex = as.character(sex_fac),
         n = as.integer(n)) %>%

  ggplot( mapping = aes(x = ifelse(test = sex_fac == "Male", yes = -n, no = n), 
                     y = age, fill = sex)) +
  geom_col() +
  scale_x_symmetric(labels = abs) +
  labs(x = "Population ",
       title = "Age distribution in the sample") +
  scale_y_discrete(breaks = c(19, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 82)) +
  
  theme(
    plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5),
    panel.background = element_rect(fill = "white"),
    panel.grid.major.y = element_line(size = 0.5, linetype = 'solid',
                                      colour = "grey") 
  )
```
The visualisation of age distribution separated by sex supports the insight, that there is no significant difference or trend in age distribution.

```{r , echo=FALSE, out.width="100%"}
boxplot_happy <- boxplot_age(happy_fac, age, sex_fac) +
  labs(title = "Range of age for the level of happiness",
       fill = "age") 

boxplot_satisfaction <- boxplot_age(satisfaction_fac, age, 0) +
  labs(title = "Range of age by satisfaction") +
  theme(legend.position = "none")


grid.arrange(boxplot_happy, boxplot_satisfaction, nrow = 1)
```
The boxplots show the distribution of age within the different levels of happiness and satisfaction. On the left graph it can be seen, that the median age increases, the less satisfied a person is. In the left graph it can be seen, that people who are "not happy at all" tend to be much older by median, than people who are very happy. For a less biased picture, we decided to split the level of happiness into male and female. It can be seen, that this does not make so big of a difference. However, a switch in the median age is observable, the less happy a person gets. The right boxplot shows that people with a satisfaction-level of 1 and 2 are almost solely over the age of 50. We can also note, that with satisfaction-levels of 3 and 4, the age is also quite high except for the lower 25 percentile in age and the lower outliers. Quite striking are the variances in the satisfaction-levels from 5 to 10, which span the whole age spectrum, although in general we can say that the higher the satisfaction-level the lower the median age

### Marital status
```{r , echo=FALSE, out.width="100%"}
barplot_var(marst_fac) +
  labs(title = "Marriage distribution")
```
Since it is not possible, to put the marital status in some kind of hierarchy, it can be considered a nominal scaled variable. The graph shows the distribution of people regarding their legal marital status. It can be seen, that the wide majority (60%) is married. The second and third highest population is formed by people who are single or have never been married (19%), and people who are widowed (15%).

The following mosaic plots are an attempt of a causal link between the marriage status, happiness and life satisfaction 
```{r , echo=FALSE, out.width="100%"}
romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(happy_fac, marst_fac), fill = happy_fac)) +
  
  labs(title ="Comparison of happiness in life and marital status",
       fill = "Scale of satisfaction") +
  mosaic_theme
```
It can be seen, that the widowed people are generally the ones who are rather not, or not happy at all. The single and married people are generally the biggest peopulation of people who are "very happy". 

```{r , echo=FALSE, out.width="100%"}
romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(satisfaction_group, marst_fac), fill = satisfaction_group)) +
  
  labs(title ="Comparison of satisfaction in life and marital status",
       fill = "Scale of satisfaction") +
  mosaic_theme
```
The distribution of "very satisified" people is quiet similar to the one seen in the previous plot. The same counts for the "not very" or "not satisfied at all", with widowed people making up the largest population.


### Additional variables
```{r , echo = FALSE, out.width="100%"}

activity_fun <- function(var, var_char){
  romania %>% select(happy, {{var}}) %>% rename(member = {{var}}) %>% mutate(cat = {{var_char}})
}

bind_rows( activity_fun(member_activity, "an activity"),
           activity_fun(member_religion, "a religion"),
           activity_fun(member_selfhelp, "a selfhelp group"),
           activity_fun(member_charity, "a charity"),
           activity_fun(member_labor_union, "a labor union")) %>%
  
  group_by(member, cat, happy) %>%
  summarize(n = n()) %>%
  mutate(perc = n/sum(n)) %>%
  
  ggplot(aes(x = as_factor(member), y = perc, fill = as_factor(happy))) +
  geom_bar(stat = "identity") +
  labs(fill = "Level of Happiness",
       y = "Distribution (%)",
       title = "Member of ...") +
  
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle=90),
    #axis.title.y = element_blank(),
    panel.background = element_rect(fill = "white"),
    panel.grid.major.y = element_line(size = 0, linetype = 'solid',
                                      colour = "grey") ,
    plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5) 
    
  ) +
  
  scale_y_continuous(labels = scales::percent,
                     breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
  
  facet_grid( ~ cat) 
```
These additional variables also allow a little bit of insight into the data. Starting off with charitable causes we can see that those who mentioned being a member of a charitable organisation reported to be quite happy or very happy more often. 

Being a member of a labor union also seems to have a certain connection to happiness as union members more often reported to be quite or very happy as opposed to non-members. 

Interestingly, being a member of a religious organisation doesn't seem to increase happiness for all participants. It can be observed that those who are religious more often reported to be not very happy but at the same time religious respondents more often reported to be very happy. One way of interpreting this would be to assume that being religious could have a diverging effect on people and either increase or decrease their happiness according to some other external variable. 

Looking at the variable of being a member of a self-help group, the graphs don't diverge as much as for other variables. Those who are members of a self-help group have a little more frequently reported to be quite happy than those who are not, but the effect is very small. 

Finally, being a member of an activity. This seems to be connected to the effect of happiness as those who have reported to be member of any sort of activity rarely mentioned to be not very happy or not at all happy. Over 90% of respondents who mentioned to be member of an activity reported to be either very or at least quite happy.


# Social Capital
> The literature shows that Social Capital is an important factor for increasing the level of SWB. For the trust dimension of social capital you may use the variable asking whether people can generally be trusted or not, for the weak ties dimension you could use the sum of the variables asking whether one is a member of ...

For the following section, we shall have a look at how the subjective well-being (SWB), namely general happiness and life satisfaction, are linked to Social Capital
In order to take a closer look at the SWB, we shall take the term of the Social Capital into account. The literature shows that Social Capital is an important factor for increasing the level of SWB. But first of all, what is Social Capital?
Social capital can be seen as "a positive product of human interaction" (investopedia.com). While it can not be owned by somebody, it is the result of connections between individuals within social networks. Social capital can be seen as a base pillar for the effective functioning of social groups. The absence of Social capital can mislead a group of people to not achieve a common goal or purpose. 

Despite its undeniable value for any group of individuals, there is no consensus on how social capital can be measured directly. This leads to the conclusion, that social capital can only be expressed through other indicators. The European Value Study (EVS) includes several indicators which can help to determine a countries Social Capital.
In the following, we are going to consider trust as a key dimension for social capital. The EVS sees the trust variable as an indication whether most people can be trusted or not. in particular, the people participating in the survey get asked the following question: Generally speaking, would you say that most people can be trusted or that you can’t be too careful in dealing with people? 
The answer is then separated into two possible answers (1) "Most people can be trusted" and (2) "Can't be too careful". In the following diagram, we are going to provide an overview of the responses of the qualitative variable.

The following pie chart depicts the distribution of the two levels of trust in Romania
```{r , echo = FALSE, out.width="100%"}
trust_summary <- romania %>%
  
  group_by(trust_fac) %>%
  summarise(n = n()) %>%
  mutate(prop = round(n/sum(n)*100,2))

trust_plot <- trust_summary %>%
  
  ggplot(aes(x = "", y = prop, fill = trust_fac)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  geom_text(aes(y = prop, label = n), color = "black", position = position_stack(vjust = 0.5)) +
  
  labs(title = "Dimensions of trust",
       fill = "Respones to the question") +
  
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.background = element_rect(fill = "white"),
    panel.grid.major.y = element_line(colour = "white"),
    plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5)
    )

grid.arrange(trust_plot, tableGrob(trust_summary),  heights = c(2, 0.5))
```
As we can see from the pie chart and the table, people in Romania are generally rather careful. The vast majority (approx. 85%) expresses their trust in people on a level of "can't be too careful. This rough overview already gives the impression, that the level of Social Capital is rather low in Romania.

The following graph provides an overview on how trust and happines in life, as well as trust and satisfaction are eventually linked.
```{r , echo = FALSE, out.width="100%"}
bind_rows(trust_var_summary(happy_fac, "Happiness"),
          trust_var_summary(satisfaction_fac, "Satisfaction")) %>%

  ggplot(aes(x = as_factor(member), y = prop, fill = as_factor(trust_fac))) +
  geom_bar(stat = "identity") +
  labs(fill = "Level of trust",
       y = "Distribution (%)",
       title = "Impact of the level of trust on ...") + 
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle=90),
    #axis.title.y = element_blank(),
    panel.background = element_rect(fill = "white"),
    panel.grid.major.y = element_line(size = 0, linetype = 'solid',
                                      colour = "grey") ,
    plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5) 
    
  ) +
  
  scale_y_continuous(labels = scales::percent,
                     breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
  
  facet_grid( ~ cat, scales="free_x") 
```

Looking at the graph, it is hard to establish a clear trend within the data.
Starting with the "Happiness" part of the diagram, it can roughly be said, 
that those who are very or quite happy with their lives tend to trust their
fellow citizens more on average.

A similar trend cannot really be observed in the case for satisfaction.
Here, dissatisfied participants seem to trust their fellow citizens more.
While there are differences in the level of trust, it's not possible to 
observe a trend.

Furthermore it needs to be stated, that the overall level of trust rarely 
exceeds 20% with a maximum of 30% being reached only once.

Besides the trust factor, analyzing "weak ties" can also help to get an impression of the Social Capital among the Romanian people. The term weak ties implies connections among individuals which one does not know very well, but by whom one is surrounded on a regular basis. In the EVS, the interviewers asked the participants weather they are a member of various groups. Let us therefor first have a very general overview of how the membership in any group can have on happiness and or life satisfaction. 
*Note: for a better overview, the level of satisfaction has been grouped into 1: 'Not satisfied at all', 2-5: 'Not very satisfied', 6-9: 'Quite satisfied', 10: 'Very satisfied'.*
```{r , echo = FALSE, out.width="100%"}
member_happy <- ties_var_summary(happy_fac, "Happiness") +
  labs(title = "Level of happiness ",
       fill = "Level of happiness",
       subtitle = "for (non) members of any group")
  
member_satisfaction <- ties_var_summary(satisfaction_group, "Satisfaction") +
  labs(title = "Level of satisfactions",
       fill = "Level of satisfaction",
       subtitle = " for (non) member of any group")

grid.arrange(member_happy, member_satisfaction, nrow = 1)
```


It can be seen, that on average members of any given organisation or institution
are happier and more satisfied, than individuals who are not.
This effect doesn't seem to change when looking at general happiness or life
satisfaction.



```{r , echo = FALSE, out.width="100%"}
bind_rows( fun_happy(happy, member_activity, "an activity"),
           fun_happy(happy, member_religion, "a religion"),
           fun_happy(happy, member_selfhelp, "a selfhelp group"),
           fun_happy(happy, member_charity, "a charity"),
           fun_happy(happy, member_labor_union, "a labor union"),
           fun_happy(happy, member_sports, "a sports group")) %>%
  
  group_by(member, cat, happy) %>%
  summarise(n = n()) %>%
  mutate(perc = n/sum(n)) %>%
  
  ggplot(aes(x = as_factor(member), y = perc, fill = as_factor(happy))) +
  geom_bar(stat = "identity") +
  labs(fill = "Level of Happiness",
       y = "Distribution (%)",
       title = "Lebel of happiness, given somebody is a member of ...") +
  
  scale_y_continuous(labels = scales::percent,
                     breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
  
  facet_grid( ~ cat) +
  
  theme_cat
```
Starting off with charitable causes we can see that those who mentioned being 
a member of a charitable organisation reported to be quite happy or very happy 
more often.

Being a member of a labor union also seems to have a certain connection to
happiness as union members more often reported to be quite or very happy as 
opposed to non-members.

Interestingly, being a member of a religious organisation doesn't seem to 
increase happiness for all participants. It can be observed that those who are
religious more often reported to be not very happy but at the same time 
religious respondents more often reported to be very happy. One way of 
interpreting this would be to assume that being religious could have a diverging
effect on people and either increase or decrease their happiness according to 
some other external variable.

Looking at the variable of being a member of a self-help group, the graphs don't
diverge as much as for other variables. Those who are members of a self-help
group have a little more frequently reported to be quite happy than those who are
not, but the effect is very small.

Looking at sports groups, the effect on happiness seems to be surprisingly
large. Those who reported to be members of sports groups are to a large extent
either very happy or at least quite happy overall. Those two groups together 
constitute over 90% of those reporting to be member of a sports group or team.

Finally, being a member of an activity. This seems to be connected to the effect
of happiness as those who have reported to be member of any sort of activity 
rarely mentioned to be not very happy or not at all happy. Over 90% of respondents
who mentioned to be member of an activity reported to be either very or at least
quite happy. 
It can be assumed, that this effect is similar to the one observed for sports
groups, as the graph for overall activities strongly mirrors the one for sports
groups.

We assume that weak ties also appear in the neighborhood. Since neighbors are in some way silent, but steady companions, we find it highly important to look at what impact a certain neighborhood can have on the the trust the questioned people have in them.
```{r , echo = FALSE, out.width="100%"}
bind_rows( fun_happy(trust_neighbor, neighbours_diffrace, "have a different race"),
           fun_happy(trust_neighbor, neighbours_drinkers, "are drinkers"),
           fun_happy(trust_neighbor, neighbours_immig, "are immigrants"),
           fun_happy(trust_neighbor, neighbours_drugs, "are drugaddicts"),
           fun_happy(trust_neighbor, neighbours_homosex, "are homosexuals")) %>%
  
  group_by(member, cat, trust_neighbor) %>%
  summarise(n = n()) %>%
  mutate(perc = n/sum(n)) %>%
  
  ggplot(aes(x = as_factor(member), y = perc, fill = as_factor(trust_neighbor))) +
  geom_bar(stat = "identity") +
  labs(fill = "Level of trust in neighbours",
       y = "Distribution (%)",
       title = "Level of trust in neighbours, given they ...") +
  
  scale_y_continuous(labels = scales::percent,
                     breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
  
  facet_grid( ~ cat) +
  
  theme_cat
```
Starting off with drinking neighbors. To most people it doesn't really seem
to matter if their neighbors are drinkers or not. The two graphs barely differ
from each other. There is a small group of respondents that responds with
"trust somewhat" as opposed to "trust completely" if their neighbors are 
drinkers, but the effect is too small to be investigated further.
 
Being a drug addict however, seems to have a more significant effect. The picture
is similar to drinking, but a larger percentage of respondents reports to not
trust their neighbors very much if they are drug addicts.
 
The case for homosexuality however is an interesting one. There seems to be 
a rather large group of respondents that chooses not to trust their neighbors
very much as opposed to trusting them somewhat, if they happen to be homosexuals. 
On the other hand, there is also a group of respondents which increase the
trust in their neighbors from trusting them somewhat to trusting them completely.
Having homosexual neighbors therefore seems to have a split effect on the 
Romanian citizens, depending on an external variable.
 
Having immigrant neighbors seems to enhance the trust that Romanian citizens
have in them. This seems to be a uniform effect for all citizens. There is a 
larger percentage of citizens reporting to trust their neighbors completely
as well more citizens trusting them at least somewhat if they happen to be 
immigrants.

Neighbors having a different race seems to polarize the Romanian people to a 
small but visible extent. There is a larger percentage of respondents reporting
to trust their neighbors completely as well as a larger percentage of citizens
not trusting their neighbors at all if they have a different race.

Furthermore, weak ties also appear within a religion. Individuals which share similar interests, such as the same god, implicitly see each other on a regular basis when attending a church service. The following two mosaic plots shall provide an overview on how the attendance of a church service might affect the level of SWB, as we assume, that weak ties have a positive effect on the Social capital and therefor on the level of SWB.
```{r , echo = FALSE, out.width="100%"}
service_happy <-  romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(happy_fac, relig_service_fac), fill = happy_fac)) +
  labs(title ="Comparison of happiness in life",
       fill = "Scale of happiness",
       subtitle = "with church service attendance") +
  mosaic_theme

service_satis <- romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(satisfaction_group, relig_service_fac), fill = satisfaction_group)) +
  
  labs(title ="Comparison of satisfaction",
       fill = "Scale of satisfaction",
       subtitle = "with church service attendance") +
  mosaic_theme

grid.arrange(service_happy, service_satis, nrow = 1)
```

There doesn't seem to be a clear connection between church attendance and
happiness in life or life satisfaction. The mosaic patterns don't differ 
very much from each other, with one exception. It can be seen, that those
who practically never attend church report to be not very happy a little 
more frequently than those who (for instance) attend church more than once
a week. This effect however is not visible when switching to life 
satisfaction. Overall, the effect doesn't seem to be strong  enough to 
speculate a connection between church attendance and happiness or satisfaction.


# Principal Component Analysis
> Try to find appropriate components for the political interest and attitude dimension, e.g. run a PCA using the variables “Interested in politics”, “Satisfaction with the political system”, “Having a democratic political system”, “Importance of democracy”, ...


## overview of variables
The key variable for our analysis is going to be the E023 - Interest in politics (interest_politics) variable. However, the survey offers more questions in regards to the attitude towards politics. 
In order to avoid misunderstanding, we want to give a quick overview of what the variables mean. 

  | **id**  | **variable**          | **explaination**                                  |
  |---------|-----------------------|---------------------------------------------------|
  | E023    | intrests_politics     | How interested would you say you are in politics? |
  | E025    | politics_petition     | Signing a petition                                |
  | E026    | politics_boycott      | Joining in boycotts                               |
  | E027    | politics_demo         | Attending lawful demonstrations                   |
  | E028    | politics_strikes      | Joining unofficial strikes                        |
  | E111_01 | politics_satisfaction | Satisfaction with the political system            |
  | E117    | politics_democracy    | Having a democratic political system              |
  | E235    | importance_democracy  | Importance of democracy                           |
  
The variables in the following graph are going to be key elements in the following principal components analysis.
```{r , echo = FALSE, out.width="100%"}
politics_variables <- romania %>% 
  select(intrests_politics, politics_petition, 
         politics_boycott,
         politics_demo,
         politics_strikes,
         
         politics_satisfaction, 
         politics_democracy,
         importance_democracy 
  ) 
politics_variables_plot <- politics_variables %>% rownames_to_column()

politics_var <- function(varchar) {
  politics_variables_plot %>%
  mutate_all(function(x) droplevels(as_factor(x))) %>% 
  melt(id.vars = "rowname", variable.name = "factor", value.name = "level") %>%
  
  group_by(factor, level) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  mutate(freq_cum = revcumsum(freq)) %>%
  filter(factor == {{varchar}}) %>%
  
  ggplot(aes(y = freq, x = factor, fill = level)) +
    geom_bar(postition = "dodge", stat = "identity") +

geom_text(aes(y = freq_cum, label = level), vjust = 1.5, colour = "white", size = 3) +
scale_y_continuous(labels = scales::percent) +

theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.background = element_rect(fill = "white"),
  panel.grid.major.y = element_line(size = 0.5, linetype = 'solid',
                                    colour = "grey"),
  plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.1),
  legend.position = "none"
)
}

grid.arrange(politics_var("intrests_politics" ), politics_var("politics_petition"), politics_var("politics_boycott"), politics_var("politics_demo"), ncol = 4)
grid.arrange(politics_var("politics_strikes"), politics_var("politics_satisfaction"), politics_var("politics_democracy"), politics_var("importance_democracy"), ncol = 4)

summary(pc.politics)
```


INTERPRETATION
Choosing 5 PCs
Reason: With 5PCs around 80% of the variance is covered.

Vielleicht kurz über verteilung reden.


```{r , echo = FALSE, out.width="100%"}

pc.politics <-  politics_variables %>% prcomp( scale = TRUE)

fviz_eig(pc.politics, addlabels = TRUE)

grid.arrange(fviz_pca_ind(pc.politics, axes = c(1,2), label = "var", repel = TRUE),
             fviz_pca_ind(pc.politics, axes = c(1,3), label = "var", repel = TRUE), 
             fviz_pca_ind(pc.politics, axes = c(2,3), label = "var", repel = TRUE),
             fviz_eig(pc.politics, addlabels = TRUE),
             ncol = 2)

grid.arrange(fviz_pca_biplot(pc.politics, axes = c(1,3), label = "var", repel = TRUE),
             fviz_pca_biplot(pc.politics, axes = c(1,2), label = "var", repel = TRUE),
             ncol = 2)
grid.arrange(fviz_pca_biplot(pc.politics, axes = c(1,4), label = "var", repel = TRUE),
             fviz_pca_biplot(pc.politics, axes = c(1,5), label = "var", repel = TRUE),
             ncol = 2)
```


Bitte interpretieren.






