---
title: "Happiness Economics - Group: Romania"
author: "[Sören Schwabbauer](soeren.schwabbauer@uibk.ac.at), [David Hollenstein](david.hollenstein@student.uibk.ac.at), [Alexander Hanser](alexander.hanser@student.uibk.ac.at), [Jürgen Bildstein](juergen.bildstein@student.uibk.ac.at)"
#date: "2022-10-25"
output: 
  html_document: 
    css: style.css
    
    toc: true
    toc_depth: 3
    toc_float: true
    
    number_sections: true

---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# load libraries
library(knitr)
library(dplyr)
library(haven)
library(ggplot2)
library(ggmosaic)
library(lazyeval)
library(gridExtra)
library(ggmosaic)
library(lemon)
library(reshape2)
library(spatstat.utils)
library(tibble)
library(webr)
library(patchwork)
library(factoextra)
library(sjlabelled)
if (dir.exists("G:/Geteilte Ablagen/")) {
  
  INPUT = "G:/Geteilte Ablagen/data_analytics/01_data_build/OUTPUT/"
  
} else if (dir.exists("G:/Shared drives/")) {
  
  INPUT = "G:/Shared drives/data_analytics/01_data_build/OUTPUT/"
  
}
# load dataframe
load(paste0(INPUT, "romania.rda"))
```


```{r functions & plots for task 2 , echo = FALSE, out.width="100%"}
##### define themes and create functions for plotting ##########################
# define theme for mosaic ######################################################
barplot_var_gender <- function(var,sex){
  romania %>%
    filter(sex_fac == paste0({{sex}})) %>%
    ggplot(aes(x= {{var}}, y= ..count.. , fill = {{var}})) +
    geom_bar() +
    labs(x = "",
         y = "total number") +
    geom_text(stat = "count", aes(label= ..count..)) +
    theme(
      legend.position = "none",
      axis.title.x = element_blank(),
      panel.background = element_rect(fill = "white"),
      panel.grid.major.y = element_line(size = 0.5, linetype = 'solid',
                                        colour = "grey") ,
      plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5)
      
    )
}

mosaic_theme <-   theme( 
  #legend.position = "none",
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  axis.text.x = element_text(angle=90, size = 7),
  axis.text.y = element_text(size = 7),
  panel.background = element_rect(fill = "white"),
  panel.grid.major.y = element_line(size = 0, linetype = 'solid',
                                    colour = "white") ,
  legend.position = "none",
  plot.title = element_text(color="black", size= 8, face="bold.italic", vjust = 0.5)
) 
  
# define function, incl. theme for barplots ####################################
barplot_var <- function(var){
  romania %>%
    ggplot(aes(x= {{var}}, y= ..count.. , fill = {{var}})) +
    geom_bar() +
    labs(x = "",
         y = "total number") +
    geom_text(stat = "count", aes(label= paste0(..count.., " (", round(..count../nrow(romania),4)*100 , "%)")), vjust = -0.5, size = 3) +
  
    theme(
      legend.position = "none",
      axis.title.x = element_blank(),
      panel.background = element_rect(fill = "white"),
      panel.grid.major.y = element_line(size = 0.5, linetype = 'solid',
                                        colour = "grey") ,
      plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5)
      
    )
}
boxplot_for_barplot <- function(var){
  romania %>%
    ggplot(aes(y = as.numeric({{var}}))) +
    geom_boxplot(width = 0.5) +
    coord_flip() +
    
    theme(
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      panel.background = element_rect(fill = "white"),
      panel.grid.major.y = element_line(size = 0.5, linetype = 'solid',
                                        colour = "white"),
      plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5)
    ) 
}
boxplot_age <- function(var1, var2, var3){
  romania %>% 
    ggplot(aes(x = {{var1}}, y = {{var2}})) +
    geom_boxplot(aes(fill = {{var3}})) +
    
    theme(
      axis.title.x = element_blank(),
      axis.text.x = element_text(angle=90),
      axis.ticks.x = element_blank(),
      #axis.title.y = element_blank(),
      #axis.text.y = element_blank(),
      #axis.ticks.y = element_blank(),
      panel.background = element_rect(fill = "white"),
      panel.grid.major.y = element_line(size = 0.5, linetype = 'solid',
                                        colour = "grey"),
      plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5)
      
    ) +
    scale_y_continuous(breaks = c(10, 20, 30, 40, 50, 60, 70, 80))
}
```

```{r functions & plots for task 3 , echo = FALSE, out.width="100%"}
### function for impact of the level of trust on 
trust_var_summary <- function(var, var_char){
  romania %>% select(trust_fac, {{var}}) %>% rename(member = {{var}}) %>% mutate(cat = {{var_char}}) %>%
    group_by(member, cat, trust_fac) %>%
    summarise(n = n()) %>%
    mutate(prop = n/sum(n)) 
}
### function + plot for general membership
ties_var_summary <- function(var, var_char){
  romania %>% select({{var}},contains("member_")) %>% rename(member = {{var}}) %>% melt() %>%
    group_by(value, member) %>%
    summarise(n = n()) %>%
    mutate(prop = n/sum(n)) %>%
    
    mutate(value = replace(value, value == 1, "member"),
           value = replace(value, value == 0, "no member"),
           value = as_factor(value)) %>%
    
    ggplot(aes(x = (value), y = prop, fill = as_factor(member))) +
    geom_bar(stat = "identity") +
    labs(y = "Distribution (%)") + 
    theme(
      axis.title.x = element_blank(),
      axis.text.x = element_text(angle=0),
      #axis.title.y = element_blank(),
      panel.background = element_rect(fill = "white"),
      panel.grid.major.y = element_line(size = 0, linetype = 'solid',
                                        colour = "grey") ,
      plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5) ,
      plot.subtitle = element_text(color = "black", size = 10, face = "italic")
      
    ) +
    
    scale_y_continuous(labels = scales::percent,
                       breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) 
}
### function for each membership & type of neighbor + theme for the plots
fun_happy <- function(cat, var, var_char){
  romania %>% select({{cat}}, {{var}}) %>% rename(member = {{var}}) %>% mutate(cat = {{var_char}}) %>%
    
    mutate(member = as.character(as_factor(member)),
           member = replace(member, member == "Mentioned", "yes"),
           member = replace(member, member == "Not mentioned", "no"))
}
theme_cat <-   theme(
  axis.title.x = element_blank(),
  axis.text.x = element_text(angle=0),
  #axis.title.y = element_blank(),
  panel.background = element_rect(fill = "white"),
  panel.grid.major.y = element_line(size = 0, linetype = 'solid',
                                    colour = "grey") ,
  plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5) 
)
```

# Download data
>  Download the data for the country you choose. You also find the official variable description file in the corresponding folder.
Done.

___
# First overview of data
> Get acquainted with the data (rename and/or recode variables). The main variables with which we are going to work are measures of subjective well-being (SWB), namely general happiness and life satisfaction. Are these two variables comparable measures of SWB? How do these variables correlate with personal characteristics like income, health, age, marital status, etc.? Find suitable ways to show some possible (not necessarily causal) relationships.
## A170 satisfaction in life
```{r , echo = FALSE, out.width="100%"}
 summary(romania$satisfaction)
```
The summary command allows us to have a rough overview of the variable A170 - satisfaction in life. The variable is scaled from 1 to 10, with 10 being the highest level of satisfaction. Since one can rank the level of satisfaction (e.g: a level of 8 being higher ranked than a level 2), but the distance between the levels is subjective (e.g: a person on a level 8 is not necessarily twice as happy as a person on the level 4) Life satisfaction can be considered an ordinarily scaled variable. 
The summary command shows, that everybody has replied to to questions (no NA's). Another conclusion which can be drawn from the summary command is the average level of satisfaction. With a median level of 8, and a mean of 7.5, the Romanian people are generally not extremely satisfied, but also not unsatisfied with their life as a whole. In addition to that, it can be seen, that the half of the asked population ranks themselves between a 6 and a 9.

The following plot allows a look at the distribution of satisfaction
```{r , echo = FALSE, out.width="100%"}
bar_satiscation <- barplot_var(satisfaction_fac) 
box_satiscation <- boxplot_for_barplot(satisfaction) +
  labs(title = "Overall life satisfaction") 
grid.arrange(box_satiscation, bar_satiscation, nrow = 2, heights = c(0.5,2))
```
The barplot on the distribution of satisfaction in life adds additional information to the summary command. As one can see, most people can identify with the highest level "satisfied" . It remains unclear, why there is such a rapid drop one level below. Furthermore it can be seen, that the lower 25% are much more distributed (from 2 to 5), whereas "Satisfied" contains all the upper 25% of the counts. 

## A008 Feeling of happiness
```{r , echo = FALSE, out.width="100%"}
summary(romania$happy)
```
Also the variable happy only contains interpretable values. Neither has nobody not answered, nor has the question being skipped, or other other problems occurred. The variable is scaled from 1 to 4. 1 indicates "very happy", 4 indicates "not at all happy". Identical to satisfaction, the feeling of happiness counts as a originally scaled variable.

The following barplot allows a closer look at the distribution of happiness within # the questioned people in Romania
```{r , echo=FALSE, out.width="100%"}
barplot_var(happy_fac) +
  labs(title = "Overall feeling of happiness")
```
From the barplot one can conclude, that most people (approx. 56%) are "quite happy", one fifth of the questioned population are "very happy" and roughly the same amount of people are "not very happy", or "not at all happy"


## Univariate and multivariate analysis of SWB Factors
In the following section we are going to provide a comparison of the two key variables with other variables. 

### Income
```{r , echo = FALSE, out.width="100%"}
summary(romania$income_scale)
```
The variable income was evaluated by showing the questioned households a range of income groups within their country, of which the participants had to select one. The income then got scaled from 1 (the 1st decile) and 10 (the highest decile).

The following two plots allow an insight in the income distribution of Romania
```{r , echo = FALSE, out.width="100%"}
bar_income <- barplot_var(income_scale_fac) +
    theme(axis.text.x = element_text(angle=90))
box_income <- boxplot_for_barplot(income_scale) +
  labs(title = "Income distribution") 
grid.arrange(box_income, bar_income, nrow = 2, heights = c(0.5,2))
```
It can be seen, that the distribution is right skewed. This indicates, that the vast majority belongs to a lower income group. The boxplot shows, that 50% of the people lay in between the 3rd and the 5th decile.

The following mosaic plots shall provide an overview of the two main variables and the scaled income.
```{r , echo = FALSE, out.width="100%"}
inc_happy <-  romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(happy_fac, income_scale_fac), fill = happy_fac)) +
  
  labs(title ="Comparison of happiness in life and income",
       fill = "Scale of happiness") +
  mosaic_theme
  
inc_satis <- romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(satisfaction_group, income_scale_fac), fill = satisfaction_group)) +
  
  labs(title ="Comparison of satisfaction in life and income",
       fill = "Scale of satisfaction") +
  mosaic_theme
grid.arrange(inc_happy, inc_satis, nrow = 1)
```
The two mosaic plots allow a bivariate exploratory analysis among the variables income and happiness, as well as income and satisfaction. The comparison between income and satisfaction in life shows, that the group with the lowest income is the group has more "very happy" people, than the following 3 decile's. However by grouping "quite happy" and "very happy" into one category, as suggested by the second decile, it can then be seen that the lower three deciles make up for the lowest share. When analyzing the top 30% of income earners, we can see that almost everybody is at least "quite happy". Also worth noting is that the top decile group of earners has less "very happy" people as decile group 7,8 & 9.

For a better overview, we grouped the levels of satisfaction into 1 = "Not satisfied at all, 2-5 = "not very satisfied", 6-9 = "quiet satisfied" and 10  = very satisfied.Comparing the satisfaction and the income, the group with the lowest income, again has one of the highest rates of satisfaction. Tough it should also be mentioned, that they also share one of the highest rates of Dissatisfaction. Once again it shows, that a higher income rules out the chance of being "not satisfied at all". At the same time, the top 10% income group accounts for the lowest amount of very satisfied people. 


### Health
```{r , echo=FALSE, out.width="100%"}
bar_health <- barplot_var(health_fac) 
box_health <- boxplot_for_barplot(health) +
  labs(title = "Health distribution")
grid.arrange(box_health, bar_health, nrow = 2, heights = c(0.5,2))
```
The average citizen seems to be in rather good health condition. Most of the answers group around the "good" health answer. The second most frequent answer is the "fair" health response. A very small percentage of respondents report being of "poor" or "very poor" health. 

```{r , echo=FALSE, out.width="100%"}
health_happy <-  romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(happy_fac, health_fac), fill = happy_fac)) +
  
  labs(title ="Comparison of happiness in life and health",
       fill = "Scale of happiness") +
  mosaic_theme
health_satis <- romania %>%
  
  ggplot() +
  geom_mosaic(aes(x =  product(satisfaction_group, health_fac), fill = satisfaction_group)) +
  
  labs(title ="Comparison of satisfaction in life and health",
       fill = "Scale of happiness") +
  mosaic_theme
grid.arrange(health_happy, health_satis, nrow = 1)
```
These mosaic plots show a connection between health of an individual and the satisfaction with life and overall happiness. Looking at happiness in life first, what stands out is, that those with poor and very poor health are to a large extent not very happy. This also translates to overall life satisfaction. Those with poor health are to a large extent not very satisfied. The opposite to this observation also holds true. Those with good and very good health are to a very large extent either very happy or quite happy. Respectively, those with good and very good health are also quite satisfied and very satisfied.

### Age
```{r , echo=FALSE, out.width="100%"}
summary(romania$age)
```
The summary command tells us the mean and the median age. Bothe are around 50. With the mean and the median age laying close together, one can say, that  the distribution is rater equal. Since the age scaling end at the age of 82, one can not say, how old the oldest person in the dataframe is. The youngest however is at the age of 19.

In order to get a brief overview of the age distribution, a population pyramid can help.
```{r , echo=FALSE, out.width="100%"}
romania %>% 
  group_by(age, sex_fac) %>%
  summarize(n = n()) %>% 
  mutate(age = as.character(age),
         sex = as.character(sex_fac),
         n = as.integer(n)) %>%
  ggplot( mapping = aes(x = ifelse(test = sex_fac == "Male", yes = -n, no = n), 
                     y = age, fill = sex)) +
  geom_col() +
  scale_x_symmetric(labels = abs) +
  labs(x = "Population ",
       title = "Age distribution in the sample") +
  scale_y_discrete(breaks = c(19, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 82)) +
  
  theme(
    plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5),
    panel.background = element_rect(fill = "white"),
    panel.grid.major.y = element_line(size = 0.5, linetype = 'solid',
                                      colour = "grey") 
  )
```
The visualisation of age distribution separated by sex supports the insight, that there is no significant difference or trend in age distribution.

```{r , echo=FALSE, out.width="100%"}
boxplot_happy <- boxplot_age(happy_fac, age, sex_fac) +
  labs(title = "Range of age for the level of happiness",
       fill = "age") 
boxplot_satisfaction <- boxplot_age(satisfaction_fac, age, 0) +
  labs(title = "Range of age by satisfaction") +
  theme(legend.position = "none")
grid.arrange(boxplot_happy, boxplot_satisfaction, nrow = 1)
```
The boxplots show the distribution of age within the different levels of happiness and satisfaction. On the left graph it can be seen, that the median age increases, the less satisfied a person is. In the left graph it can be seen, that people who are "not happy at all" tend to be much older by median, than people who are very happy. For a less biased picture, we decided to split the level of happiness into male and female. It can be seen, that this does not make so big of a difference. However, a switch in the median age is observable, the less happy a person gets. The right boxplot shows that people with a satisfaction-level of 1 and 2 are almost solely over the age of 50. We can also note, that with satisfaction-levels of 3 and 4, the age is also quite high except for the lower 25 percentile in age and the lower outliers. Quite striking are the variances in the satisfaction-levels from 5 to 10, which span the whole age spectrum, although in general we can say that the higher the satisfaction-level the lower the median age

### Marital status
```{r , echo=FALSE, out.width="100%"}
barplot_var(marst_fac) +
  labs(title = "Marriage distribution")
```
Since it is not possible, to put the marital status in some kind of hierarchy, it can be considered a nominal scaled variable. The graph shows the distribution of people regarding their legal marital status. It can be seen, that the wide majority (60%) is married. The second and third highest population is formed by people who are single or have never been married (19%), and people who are widowed (15%).

The following mosaic plots are an attempt of a causal link between the marriage status, happiness and life satisfaction 
```{r , echo=FALSE, out.width="100%"}
romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(happy_fac, marst_fac), fill = happy_fac)) +
  
  labs(title ="Comparison of happiness in life and marital status",
       fill = "Scale of satisfaction") +
  mosaic_theme
```
It can be seen, that the widowed people are generally the ones who are rather not, or not happy at all. The single and married people are generally the biggest peopulation of people who are "very happy". 

```{r , echo=FALSE, out.width="100%"}
romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(satisfaction_group, marst_fac), fill = satisfaction_group)) +
  
  labs(title ="Comparison of satisfaction in life and marital status",
       fill = "Scale of satisfaction") +
  mosaic_theme
```
The distribution of "very satisfied" people is quiet similar to the one seen in the previous plot. The same counts for the "not very" or "not satisfied at all", with widowed people making up the largest population.


### Additional variables
```{r , echo = FALSE, out.width="100%"}
activity_fun <- function(var, var_char){
  romania %>% select(happy, {{var}}) %>% rename(member = {{var}}) %>% mutate(cat = {{var_char}})
}
bind_rows( activity_fun(member_activity, "an activity"),
           activity_fun(member_religion, "a religion"),
           activity_fun(member_selfhelp, "a selfhelp group"),
           activity_fun(member_charity, "a charity"),
           activity_fun(member_labor_union, "a labor union")) %>%
  
  group_by(member, cat, happy) %>%
  summarize(n = n()) %>%
  mutate(perc = n/sum(n)) %>%
  
  ggplot(aes(x = as_factor(member), y = perc, fill = as_factor(happy))) +
  geom_bar(stat = "identity") +
  labs(fill = "Level of Happiness",
       y = "Distribution (%)",
       title = "Member of ...") +
  
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle=90),
    #axis.title.y = element_blank(),
    panel.background = element_rect(fill = "white"),
    panel.grid.major.y = element_line(size = 0, linetype = 'solid',
                                      colour = "grey") ,
    plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5) 
    
  ) +
  
  scale_y_continuous(labels = scales::percent,
                     breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
  
  facet_grid( ~ cat) 
```
These additional variables also allow a little bit of insight into the data. Starting off with charitable causes we can see that those who mentioned being a member of a charitable organisation reported to be quite happy or very happy more often. 

Being a member of a labor union also seems to have a certain connection to happiness as union members more often reported to be quite or very happy as opposed to non-members. 

Interestingly, being a member of a religious organisation doesn't seem to increase happiness for all participants. It can be observed that those who are religious more often reported to be not very happy but at the same time religious respondents more often reported to be very happy. One way of interpreting this would be to assume that being religious could have a diverging effect on people and either increase or decrease their happiness according to some other external variable. 

Looking at the variable of being a member of a self-help group, the graphs don't diverge as much as for other variables. Those who are members of a self-help group have a little more frequently reported to be quite happy than those who are not, but the effect is very small. 

Finally, being a member of an activity. This seems to be connected to the effect of happiness as those who have reported to be member of any sort of activity rarely mentioned to be not very happy or not at all happy. Over 90% of respondents who mentioned to be member of an activity reported to be either very or at least quite happy.


# Social Capital
> The literature shows that Social Capital is an important factor for increasing the level of SWB. For the trust dimension of social capital you may use the variable asking whether people can generally be trusted or not, for the weak ties dimension you could use the sum of the variables asking whether one is a member of ...
For the following section, we shall have a look at how the subjective well-being (SWB), namely general happiness and life satisfaction, are linked to Social Capital
In order to take a closer look at the SWB, we shall take the term of the Social Capital into account. The literature shows that Social Capital is an important factor for increasing the level of SWB. But first of all, what is Social Capital?
Social capital can be seen as "a positive product of human interaction" (investopedia.com). While it can not be owned by somebody, it is the result of connections between individuals within social networks. Social capital can be seen as a base pillar for the effective functioning of social groups. The absence of Social capital can mislead a group of people to not achieve a common goal or purpose. 

Despite its undeniable value for any group of individuals, there is no consensus on how social capital can be measured directly. This leads to the conclusion, that social capital can only be expressed through other indicators. The European Value Study (EVS) includes several indicators which can help to determine a countries Social Capital.
In the following, we are going to consider trust as a key dimension for social capital. The EVS sees the trust variable as an indication whether most people can be trusted or not. in particular, the people participating in the survey get asked the following question: Generally speaking, would you say that most people can be trusted or that you can’t be too careful in dealing with people? 
The answer is then separated into two possible answers (1) "Most people can be trusted" and (2) "Can't be too careful". In the following diagram, we are going to provide an overview of the responses of the qualitative variable.

The following table depicts the distribution of the two levels of trust in Romania
```{r , echo = FALSE, out.width="100%"}
trust_summary <- romania %>%
  
  group_by(trust_fac) %>%
  summarise(n = n()) %>%
  mutate(prop = round(n/sum(n)*100,2))
grid.arrange(tableGrob(trust_summary),  heights = c(1))
```
As we can see from the pie chart and the table, people in Romania are generally rather careful. The vast majority (approx. 85%) expresses their trust in people on a level of "can't be too careful. This rough overview already gives the impression, that the level of Social Capital is rather low in Romania.

The following graph provides an overview on how trust and happines in life, as well as trust and satisfaction are eventually linked.
```{r , echo = FALSE, out.width="100%"}
bind_rows(trust_var_summary(happy_fac, "Happiness"),
          trust_var_summary(satisfaction_fac, "Satisfaction")) %>%
  ggplot(aes(x = as_factor(member), y = prop, fill = as_factor(trust_fac))) +
  geom_bar(stat = "identity") +
  labs(fill = "Level of trust",
       y = "Distribution (%)",
       title = "Impact of the level of trust on ...") + 
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle=90),
    #axis.title.y = element_blank(),
    panel.background = element_rect(fill = "white"),
    panel.grid.major.y = element_line(size = 0, linetype = 'solid',
                                      colour = "grey") ,
    plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.5) 
    
  ) +
  
  scale_y_continuous(labels = scales::percent,
                     breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
  
  facet_grid( ~ cat, scales="free_x") 
```

Looking at the graph, it is hard to establish a clear trend within the data. Starting with the "Happiness" part of the diagram, it can roughly be said, that those who are very or quite happy with their lives tend to trust their fellow citizens more on average.

A similar trend cannot really be observed in the case for satisfaction. Here, dissatisfied participants seem to trust their fellow citizens more. While there are differences in the level of trust, it's not possible to observe a trend.

Furthermore it needs to be stated, that the overall level of trust rarely exceeds 20% with a maximum of 30% being reached only once.

Besides the trust factor, analyzing "weak ties" can also help to get an impression of the Social Capital among the Romanian people. The term weak ties implies connections among individuals which one does not know very well, but by whom one is surrounded on a regular basis. In the EVS, the interviewers asked the participants weather they are a member of various groups. Let us therefor first have a very general overview of how the membership in any group can have on happiness and or life satisfaction. 
*Note: for a better overview, the level of satisfaction has been grouped into 1: 'Not satisfied at all', 2-5: 'Not very satisfied', 6-9: 'Quite satisfied', 10: 'Very satisfied'.*
```{r , echo = FALSE, out.width="100%"}
member_happy <- ties_var_summary(happy_fac, "Happiness") +
  labs(title = "Level of happiness ",
       fill = "Level of happiness",
       subtitle = "for (non) members of any group")
  
member_satisfaction <- ties_var_summary(satisfaction_group, "Satisfaction") +
  labs(title = "Level of satisfactions",
       fill = "Level of satisfaction",
       subtitle = " for (non) member of any group")
grid.arrange(member_happy, member_satisfaction, nrow = 1)
```


It can be seen, that on average members of any given organisation or institution are happier and more satisfied, than individuals who are not. This effect doesn't seem to change when looking at general happiness or life satisfaction.


```{r , echo = FALSE, out.width="100%"}
bind_rows( fun_happy(happy, member_activity, "an activity"),
           fun_happy(happy, member_religion, "a religion"),
           fun_happy(happy, member_selfhelp, "a selfhelp group"),
           fun_happy(happy, member_charity, "a charity"),
           fun_happy(happy, member_labor_union, "a labor union"),
           fun_happy(happy, member_sports, "a sports group")) %>%
  
  group_by(member, cat, happy) %>%
  summarise(n = n()) %>%
  mutate(perc = n/sum(n)) %>%
  
  ggplot(aes(x = as_factor(member), y = perc, fill = as_factor(happy))) +
  geom_bar(stat = "identity") +
  labs(fill = "Level of Happiness",
       y = "Distribution (%)",
       title = "Level of happiness, given somebody is a member of ...") +
  
  scale_y_continuous(labels = scales::percent,
                     breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
  
  facet_grid( ~ cat) +
  
  theme_cat
```
Starting off with charitable causes we can see that those who mentioned being a member of a charitable organisation reported to be quite happy or very happy more often.
Being a member of a labor union also seems to have a certain connection to happiness as union members more often reported to be quite or very happy as opposed to non-members.

Interestingly, being a member of a religious organisation doesn't seem to increase happiness for all participants. It can be observed that those who are religious more often reported to be not very happy but at the same time religious respondents more often reported to be very happy. One way of interpreting this would be to assume that being religious could have a diverging effect on people and either increase or decrease their happiness according to some other external variable.

Looking at the variable of being a member of a self-help group, the graphs don't diverge as much as for other variables. Those who are members of a self-help group have a little more frequently reported to be quite happy than those who are not, but the effect is very small.

Looking at sports groups, the effect on happiness seems to be surprisingly large. Those who reported to be members of sports groups are to a large extent either very happy or at least quite happy overall. Those two groups together constitute over 90% of those reporting to be member of a sports group or team.

Finally, being a member of an activity. This seems to be connected to the effect of happiness as those who have reported to be member of any sort of activity rarely mentioned to be not very happy or not at all happy. Over 90% of respondents who mentioned to be member of an activity reported to be either very or at least quite happy. 

It can be assumed, that this effect is similar to the one observed for sports groups, as the graph for overall activities strongly mirrors the one for sports groups.

We assume that weak ties also appear in the neighborhood. Since neighbors are in some way silent, but steady companions, we find it highly important to look at what impact a  certain neighborhood can have on the the trust the questioned people have in them.
```{r , echo = FALSE, out.width="100%"}
bind_rows( fun_happy(trust_neighbor, neighbours_diffrace, "have a different race"),
           fun_happy(trust_neighbor, neighbours_drinkers, "are drinkers"),
           fun_happy(trust_neighbor, neighbours_immig, "are immigrants"),
           fun_happy(trust_neighbor, neighbours_drugs, "are drugaddicts"),
           fun_happy(trust_neighbor, neighbours_homosex, "are homosexuals")) %>%
  
  group_by(member, cat, trust_neighbor) %>%
  summarise(n = n()) %>%
  mutate(perc = n/sum(n)) %>%
  
  ggplot(aes(x = as_factor(member), y = perc, fill = as_factor(trust_neighbor))) +
  geom_bar(stat = "identity") +
  labs(fill = "Level of trust in neighbours",
       y = "Distribution (%)",
       title = "Level of trust in neighbours, given they ...") +
  
  scale_y_continuous(labels = scales::percent,
                     breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
  
  facet_grid( ~ cat) +
  
  theme_cat
```
Starting off with drinking neighbors. To most people it doesn't really seem to matter if their neighbors are drinkers or not. The two graphs barely differ from each other. There is a small group of respondents that responds with "trust somewhat" as opposed to "trust completely" if their neighbors are drinkers, but the effect is too small to be investigated further.
 
Being a drug addict however, seems to have a more significant effect. The picture is similar to drinking, but a larger percentage of respondents reports to not trust their neighbors very much if they are drug addicts.

The case for homosexuality however is an interesting one. There seems to be a rather large group of respondents that chooses not to trust their neighbors very much as opposed to trusting them somewhat, if they happen to be homosexuals. On the other hand, there is also a group of respondents which increase the trust in their neighbors from trusting them somewhat to trusting them completely.Having homosexual neighbors therefore seems to have a split effect on the Romanian citizens, depending on an external variable.
 
Having immigrant neighbors seems to enhance the trust that Romanian citizens have in them. This seems to be a uniform effect for all citizens. There is a larger percentage of citizens reporting to trust their neighbors completely as well more citizens trusting them at least somewhat if they happen to be immigrants.

Neighbors having a different race seems to polarize the Romanian people to a small but visible extent. There is a larger percentage of respondents reporting to trust their neighbors completely as well as a larger percentage of citizens not trusting their neighbors at all if they have a different race.

Furthermore, weak ties also appear within a religion. Individuals which share similar interests, such as the same god, implicitly see each other on a regular basis when attending a church service. The following two mosaic plots shall provide an overview on how the attendance of a church service might affect the level of SWB, as we assume, that weak ties have a positive effect on the Social capital and therefor on the level of SWB.
```{r , echo = FALSE, out.width="100%"}
service_happy <-  romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(happy_fac, relig_service_fac), fill = happy_fac)) +
  labs(title ="Comparison of happiness in life",
       fill = "Scale of happiness",
       subtitle = "with church service attendance") +
  mosaic_theme
service_satis <- romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(satisfaction_group, relig_service_fac), fill = satisfaction_group)) +
  
  labs(title ="Comparison of satisfaction",
       fill = "Scale of satisfaction",
       subtitle = "with church service attendance") +
  mosaic_theme
grid.arrange(service_happy, service_satis, nrow = 1)
```

There doesn't seem to be a clear connection between church attendance and happiness in life or life satisfaction. The mosaic patterns don't differ very much from each other, with one exception. It can be seen, that those who practically never attend church report to be not very happy a little more frequently than those who (for instance) attend church more than once a week. This effect however is not visible when switching to life satisfaction. Overall, the effect doesn't seem to be strong  enough to speculate a connection between church attendance and happiness or satisfaction.


# Principal Component Analysis
> Try to find appropriate components for the political interest and attitude dimension, e.g. run a PCA using the variables “Interested in politics”, “Satisfaction with the political system”, “Having a democratic political system”, “Importance of democracy”, ...

## overview of variables
The key variable for our analysis is going to be the E023 - Interest in politics (interest_politics) variable. However, the survey offers more questions in regards to the attitude towards politics. In order to avoid misunderstanding, we want to give a quick overview of what the variables mean. 

  | **id**  | **variable**          | **explaination**                                  |
  |---------|-----------------------|---------------------------------------------------|
  | E023    | intrests_politics     | How interested would you say you are in politics? |
  | E025    | politics_petition     | Signing a petition                                |
  | E026    | politics_boycott      | Joining in boycotts                               |
  | E027    | politics_demo         | Attending lawful demonstrations                   |
  | E028    | politics_strikes      | Joining unofficial strikes                        |
  | E111_01 | politics_satisfaction | Satisfaction with the political system            |
  | E117    | politics_democracy    | Having a democratic political system              |
  | E235    | importance_democracy  | Importance of democracy                           |
  
The variables in the following graph are going to be key elements in the following principal components analysis.
```{r , echo = FALSE, out.width="100%"}
politics_variables <- romania %>% 
  select(intrests_politics, politics_petition, 
         politics_boycott,
         politics_demo,
         politics_strikes,
         
         politics_satisfaction, 
         politics_democracy,
         importance_democracy 
  ) 
politics_variables_plot <- politics_variables %>% rownames_to_column()
politics_var <- function(varchar) {
  politics_variables_plot %>%
  mutate_all(function(x) droplevels(as_factor(x))) %>% 
  melt(id.vars = "rowname", variable.name = "factor", value.name = "level") %>%
  
  group_by(factor, level) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  mutate(freq_cum = revcumsum(freq)) %>%
  filter(factor == {{varchar}}) %>%
  
  ggplot(aes(y = freq, x = factor, fill = level)) +
    geom_bar(postition = "dodge", stat = "identity") +
geom_text(aes(y = freq_cum, label = level), vjust = 1.5, colour = "white", size = 3) +
scale_y_continuous(labels = scales::percent) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.background = element_rect(fill = "white"),
  panel.grid.major.y = element_line(size = 0.5, linetype = 'solid',
                                    colour = "grey"),
  plot.title = element_text(color="black", size= 12, face="bold.italic", vjust = 0.1),
  legend.position = "none"
)
}
grid.arrange(politics_var("intrests_politics" ), politics_var("politics_petition"), politics_var("politics_boycott"), politics_var("politics_demo"), ncol = 4)
grid.arrange(politics_var("politics_strikes"), politics_var("politics_satisfaction"), politics_var("politics_democracy"), politics_var("importance_democracy"), ncol = 4)
```

The graphs indicate a first rough overview of the political climate in Romania. For more than half of the people are not very interested to not at all interested in politics, which reflects in taking political actions. Only few people have signed a petition, joined a boycott, joined a lawful demonstration or even joined an unofficial strike. Nevertheless, a slight majority sees democracy as a very good idea, and highlight the importance of democracy.

The following tables provide an overview of the exact scaling for the variables. We decided to scale the variables in a way, that a higher number indicates a more positive attitude/ a higher involvement towards the variable.

```{r}
get_labels(
  politics_variables,
  attr.only = FALSE,
  values = "as.prefix",
  non.labelled = FALSE,
  drop.na = TRUE,
  drop.unused = TRUE
)
```

## Analysis {.tabset}

In order to find groups in the data, we decided to plot the dimensions among each other. In the following section, one can see a Screeplot in 4.2.1, and the different scatterplots for the first two principal components. We neglect comparing the 4th and the 5th principal component, since we find the variance covered, to be too low.

### Screeplot
```{r}
pc.politics <-  politics_variables %>% prcomp( scale = TRUE)
fviz_eig(pc.politics, addlabels = TRUE)
```

Looking at the principal components and their visualization within the screeplot it is tricky to clearly identify the number of PCs that should be considered. There is no clearly visible “elbow” which would identify the number of components that need to be considered to cover most of the variance. The first component makes up for around 32% of the explained variance. This is relatively low as compared to other datasets, but is not a matter of concern. It simply indicates that a large majority (100-32,4 = 67,6%) of observations are distributed over more than one dimension. We want to reduce the data’s dimensionality and at the same time reach 80% of explained variance, hence we are left with 3 PC’s to reach a cumulative explained variance of 63.9%. 



### scatterplot for PC1
```{r}
grid.arrange(fviz_pca_ind(pc.politics, axes = c(1,2), label = "none", repel = TRUE),
             fviz_pca_ind(pc.politics, axes = c(1,3), label = "none", repel = TRUE),
             fviz_pca_ind(pc.politics, axes = c(1,4), label = "none", repel = TRUE),
             fviz_pca_ind(pc.politics, axes = c(1,5), label = "none", repel = TRUE),
             ncol = 2)
```

From comparing these graphs, we can see, that there is a clear group forming for the first two dimensions. However, a similar group forms for the first and the fourth dimension. 


### scatterplot for PC2

```{r, echo=FALSE}
grid.arrange(fviz_pca_ind(pc.politics, axes = c(2,3), label = "none", repel = TRUE),
             fviz_pca_ind(pc.politics, axes = c(2,4), label = "none", repel = TRUE),
             fviz_pca_ind(pc.politics, axes = c(2,5), label = "none", repel = TRUE),
             ncol = 2)
```

The second and the third dimension seem to characterize a group as well. 


</div>
___


## Biplots {.tabset}

In order to identify what characterizes the groups, we want to provide some Biplots, which seemed to give us some information about the groups we might find in the data, without neglecting the level of variance we cover with the analysis.

When interpreting the biplots, one also need to take into account, how the data is scaled. For instances, the scaling of the data will be specifically noted. However, looking at the biplots between PC 1 and 2 as well as 1 and 4 a couple things become clear which are very interesting to note. 


### Biplot PC1&PC2
```{r, echo=FALSE}
fviz_pca_biplot(pc.politics, axes = c(1,2), label = "var", repel = TRUE)
```

In the Biplot between the first and the second principal component, we can see that the importance of democracy is positively correlated to the attitude of having a democratic system. Importance_democracy measures the importance, that a given respondent attributes to the concept of democracy as a whole. This is measured on a scale from 1-10 with 10 attributing the highest level of importance to the concept of democracy. That being said, it makes sense, that a respondent who thinks highly of democracy would attribute a lot of importance to the concept of democracy while simultaneously being convinced that living in a democracy is an important thing.

The remaining vectors rather form a nearly 90 degree angle towards the two mentioned vectors. Therefor it can be said, that the importance of democracy or the satisfaction with the democratic system is uncorrelated to whether somebody has attended a boycott, a strike, or a demonstration.

The interests in politics seems to also play a role in the importance for democracy, since they are positively correlated (same counts fo the attitude towards a democratic system as a whole)

Also higher interest in politics seems to lead to a higher satisfaction with the political system.


### Biplot PC1&PC4
```{r, echo=FALSE}
fviz_pca_biplot(pc.politics, axes = c(1,4), label = "var", repel = TRUE)
``` 

What sticks out in comparing the first and fourth principal component, is that a higher importance in democracy seems to be negatively correlated to the attendance of a strike. Even though this might seem to imply at first, that those who place higher value on democracy do not attend strikes very often, the opposite is actually the case. This is due to the scaling of the variable. A low numerical value in politics_strikes means that a given respondent has already participated in a strike. Therefore we can show, that those who place value on democracy can observed to go on strikes more often. This extends (to a certain extent) also to political boycotts.
</div>
___ 

# Further Weak Ties
> As Weak ties one can also take the variables “Number of active associational memberships”, “Number of inactive associational memberships”, “How important in your life: friends and acquaintances” that have to be computed by oneself. Investigate these variables and decide whether you are going to take them into your further analysis or not.

The following plot shall give an overview of the distribution on how many people are acutally in a membership.
```{r, echo=FALSE}
barplot_var(member_tot_fac) +
  labs(title ="Number of associations one is a member ") 
```

As one can see from the distribution of number of memberships, it does not make sense to keep the total number memberships as a variable, since the wide majority is not even in a single organization. Nevertheless, knowing this also helps for the further analysis. We can now add the variable "are you member in at least one organisation?". Doing so includes the variable of activities that respondents may or may not be part of in a more reasonable way. Let us have a look an the distribution of the dummy variable then.

```{r, echo=FALSE}
barplot_var(member_any_fac) +
  labs(title ="Are you a member in any association")
```

Looking at the variable of activities as a binary "are you a member of any of these organisations" variable seems to make more sense since it splits the dataset into two comparable groups. Let us therefore consider, how this weak tie influences the happiness and the life satisfaction of the Romanians.

```{r, echo=FALSE}
grid.arrange(romania %>%
               ggplot() +
               geom_mosaic(aes(x =  product(happy_fac, member_any_fac), fill = happy_fac)) +
               
               labs(title ="Comparison of happiness in life \n and member in any organisation",
                    fill = "Scale of happiness") +
               mosaic_theme,
             
             romania %>%
               ggplot() +
               geom_mosaic(aes(x =  product(satisfaction_group, member_any_fac), fill = satisfaction_group)) +
               
               labs(title ="Comparison of satisfaction in life \n and member in any organisation",
                    fill = "Scale of satisfaction") +
               mosaic_theme,
             
             nrow = 1)
```

The impact that being a member of any organisation has on life satisfaction or happiness of the Romanian population is pretty similar. For both cases we see a visible, but not overwhelming increase of respondents that report to be "very happy". For all else, there doesn't seem to be a large change in responses.

This puts the decision to include the variable into perspective since the impact that it has on the responses seems to be rather limited. After consideration, it might be better to omit the variable of activity membership for the case of Romania since the influence seems to be rather limited.        

However, we followed an additional approach, which was categorizing the membership variables into active memberships, and rather inactive memberships. The following table provides an overview of our active organisations, where we assume people to have weak ties.

  | **variables for active memberships**  | 
  |---------|
  | Belong to religious organization (given a person attends church at least once a week)    |
  | Belong to edocation, arts, music or cultural activites       |
  | Belong to venservation, the environment, ecology, animal rights    | 
  | Belong to sports or recreation    | 
  | Belong to humanitarian or charitable organization    | 
  | Belong to self-help group, mutual aid group    |
  
This leaves us with 153 Romanians in the sample. Let us have a look at what this means on happiness and satisfaction.

```{r, echo=FALSE}
grid.arrange(romania %>%
               ggplot() +
               geom_mosaic(aes(x =  product(happy_fac, member_active_fac), fill = happy_fac)) +
               
               labs(title ="Comparison of happiness in life \n and member in any organisation",
                    fill = "Scale of happiness") +
               mosaic_theme,
             
             romania %>%
               ggplot() +
               geom_mosaic(aes(x =  product(satisfaction_group, member_active_fac), fill = satisfaction_group)) +
               
               labs(title ="Comparison of satisfaction in life \n and member in any organisation",
                    fill = "Scale of satisfaction") +
               mosaic_theme,
             
             nrow = 1)
```

Here we can see a similar result to the previous plot, however, we believe, that the variable "are you an active member of an organisation" is much more reliable in regards to evaluating weak ties. However, even when only considering the memberships considered to be more active, the effect on happiness or satisfaction still remains marginal. As a consequence, we will omit the variable of membership in further analyses.


The next variable we will have a look at is the importance of friends. This can be seen as another weak tie as those who value the friends they have made in a certain area can be expected to be better integrated in their social system and be overall more content with their living situation. Let's start by looking at the overall distribution for the Romanian people:

```{r, echo=FALSE}
barplot_var(imp_friends_fac) +
  labs(title ="How important are Friends to you? ") 
```

The barplot shows, that most of the Romanian respondents seem to place at least a certain bit of importance on their friends. Most of the respondents stated that friends are "rather important" to them. Closely following up is the group for which friends are "very important". Taking these groups together, we can estimate that around 82.22% of the Romanian respondents place at least a certain bit of value on their friends. This leads us to speculate that this variable might be relevant to include in further analysis. However, in order to be sure whether we should consider this variable further, let's look at how the importance of friends impacts life satisfaction and overall happiness

```{r, echo=FALSE}
grid.arrange(romania %>%
               ggplot() +
               geom_mosaic(aes(x =  product(happy_fac, imp_friends_fac), fill = happy_fac)) +
               
               labs(title ="Comparison of happiness in life \n and importance of friendship",
                    fill = "Scale of happiness") +
               mosaic_theme, 
             
             romania %>%
               ggplot() +
               geom_mosaic(aes(x =  product(satisfaction_group, imp_friends_fac), fill = satisfaction_group)) +
               
               labs(title ="Comparison of satisfaction in life \n and importance of friendship",
                    fill = "Scale of satisfaction") +
               mosaic_theme,
             
             nrow = 1)
```

Starting with the impact that the importance of friends has on happiness, we can see that the more important friends get, the larger are the percentages of respondents claiming to be quite or very happy. However, keeping the previous illustration in mind, we need to remember that the group sizes for friend importance were rather asymmetrical, with much more respondents stating that friends would be rather important. The overall theme however still seems to be that the more important friends are to a respondent, the more happy they appear to be. We can observe a similar effect when looking at life satisfaction. The effects previously mentioned can still be seen here, although slightly less pronounced. When comparing the groups it shows that those who consider their friends to be rather or very important also seem to respond being quite or very satisfied with their lives. And although the effects might not be as pronounced as we might have hoped, we still think it pays off to keep this variable in mind when proceeding in the analysis.


# Strong Ties
> Strong ties are another important dimension of Social Capital. Use as proxy variable “How important in your life: family”.

The variable "Important in life: Family" indicates another strong tie. In order to get an overview of the variable, let us have a look at the distribution. 

```{r, echo=FALSE}
barplot_var(imp_fam_fac) +
  labs( title = "Important in life: Family")
```

As we can see from the distribution, the vast majority of the  people in Romania (91%) see their family as "very important". This is for sure not a bad thing for the Romanian people, however it is not very helpful for our further analysis, since the distribution is very unequal. Due to the low power that any analysis with this variable would have, the importance of family as a proxy for strong ties will be omitted in further analyses because of its asymmetrical distribution.

# Freedom and Control
>  As an additional important variable for life satisfaction please look at “How much freedom of choice and control”, i.e. A173. Do you find evidence for a strong association between life satisfaction or happiness and this variable?

An additional variable, that can influence life satisfaction and happiness in life is "How much freedom of choice and control" somebody has. The authors of the study describe the question as follows: some people feel they have completely free choice and control over their lives, and other people feel that what they do has no real effect on what happens to them. Please use the scale to indicate how much freedom of choice and control you feel you have over the way your life turns out?

In order to get a first overview, let us have a look at the distribution of the variable.

```{r, echo=FALSE}
bar_freedom <- barplot_var(freedom_fac)
box_freedom <- boxplot_for_barplot(freedom) +
  labs(title = "How much freedom of choice and control do you think you have?") 
grid.arrange(box_freedom, bar_freedom, nrow = 2, heights = c(0.5,2))
```

From looking at the boxplot we can see, that the median of the distribuiton is at the level of 8. Most people (32%) see themself to be very free, by answering at the highest level possible. almost 50% of the distribution chose a level the level of 9. The additional 50% of the remaining answers are distibuted in a declining distibution from 8 to 1. The lower levels, especially 1 to 4) may not have a lot of observations, however we do have quiet some oversvations for the upper levels. We therefor decided to bundle the variable as the follows: 

  | **id**  | **variable**          |
  |---------|-----------------------|
  | 1-4     | not much       |
  | 5-7    | a little     |
  | 8-9    | rather agree    |
  | 10    | A great deal     |

This leaves us with the following distribution:

```{r, echo=FALSE}
summary(as_factor(romania$freedom_group))
barplot_var(freedom_group) +
  labs(title = "How much freedom of choice and control - by groups")
```

Looking at this distribution, we can observe that most of the respondents seem to feel at least a little in control of how their lives turn out. This is something we need to keep in mind when looking at the correlations between this feeling of control and our dependent variables.


Let us now look if we can find some associations between life satisfaction or happiness in life together with the perceived control that citizens feel they have in their lives. 

```{r, echo=FALSE}
freedom_happy <-  romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(happy_fac, freedom_group), fill = happy_fac)) +
  
  labs(title ="Comparison of happiness in life \n and freedom of choice and control",
       fill = "Scale of happiness") +
  mosaic_theme
freedom_satis <- romania %>%
  ggplot() +
  geom_mosaic(aes(x =  product(satisfaction_group, freedom_group), fill = satisfaction_group)) +
  
  labs(title ="Comparison of satisfaction in life \n and freedom of choice and control",
       fill = "Scale of satisfaction") +
  mosaic_theme
grid.arrange(freedom_happy, freedom_satis, nrow = 1)
```

From looking at the mosaic plot, showing the relation between perceived freedom and happiness, a trend that we can observe is that the more people feel in control of their lives, the happier they tend to be. As previously mentioned we need to keep in mind that for those who feel not so much in control of their lives (group 1) we have a rather small sample size. This could be the reason why the trend that we can observe in groups 2 and 3 is not so much reflected in group 1. Looking at group 4 in particular, the trend also seems to be interrupted. However we can observe a higher percentage of respondents who feel like they have a lot of influence on their lives who also claim to be very happy as compared to groups 2 or 3.

Analyzing the right graph which compares satisfaction in life to freedom of choice and control, we notice a much clearer trend across the board. We could generally say that the more the Romanian people feel in control of their lives, the more satisfied they were. It needs to be noted, that especially in the group that feels not so much in control (group 1) we are working with a rather small sample size. However, this does not diminish the trend otherwise observed in the dataset and leads us to the conclusion that we will consider this variable further.

# Additional Variable: Education
> Pick one variable you think may be important and you are interested in. Argue for your chosen variable. Provide some descritptive statistics for it as well.

The variable we have chosen for this exercise is the one of marital status subject to the gender of a given respondent. The reason for this is, that the way a respondent lives at home (in a partnership or by oneself) is an important indicator of their lifestyle and can be expected to influence their happiness or satisfaction to a certain extent. However, there are limitations to this variable. We have recoded the original data and grouped the responses for marital status into two broad categories: Living in a partnership or by oneself. The original data does not contain a response for non-official partnerships which would be an interesting information to have. Furthermore we cannot tell from this data how much value a given respondent places on their partnership. Nonetheless, the following barplot displays the distribution of marital status subject to gender of a respondent.

```{r, echo=FALSE}
barplot_var(romania$sex_married)
```

We can see, that generally there are more people in our dataset that live in a relationship. This is true for male and female respondents alike. However,the distribution is not too asymmetrical, which is why the following plots will examine the impact of marital status on happiness and satisfaction.

```{r, echo=FALSE}
grid.arrange(romania %>%
               ggplot() +
               geom_mosaic(aes(x =  product(happy_fac, sex_married), fill = happy_fac)) +
               
               labs(title ="Comparison of happiness in life \n depending on sex & partnershp status",
                    fill = "Scale of happiness") +
               mosaic_theme, 
             
             romania %>%
               ggplot() +
               geom_mosaic(aes(x =  product(satisfaction_group, sex_married), fill = satisfaction_group)) +
               
               labs(title ="Comparison of satisfaction in life \n depending on sex & partnershp status",
                    fill = "Scale of satisfaction") +
               mosaic_theme,
             
             nrow = 1)
```

Starting with happiness in life, we can observe a slight increase in the frequency of responses for "quite" or "very" happy. The main difference seems to be between the two groups "partnership" and "no partnership". The difference between the two genders is rather small. The main increase happens in the percentage of respondents claiming to be "quite happy" with their situation.

For satisfaction, the picture is a lot less clear. It is almost impossible to observe a trend within the plot, as for instance as for instance the female respondents without a partnership seem to behave rather similarly as the male respondents living in a partnership. 

Since we would expect that marital status has a uniform effect on happiness or satisfaction and the effect on happiness mentioned earlier is not overwhelmingly large, we decided to not include this variable in further analysis.






